Binary companions of red giant stars in \apogee\ \DR

### 2018-02-25 paper/1-catalog/twoface-catalog.tex
numbers

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting companions,
though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker)
that delivers reliable (and often highly
multi-modal) posterior samplings for companion orbital parameters given sparse
radial-velocity data.
% Aims
Here we
perform a search for secondary companions of over 100,000 red-giant
stars observed in the
\apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief about
the amplitude of the stellar radial-velocity variation induced by the orbit \todo{do we?}.
% Results
We provide (1)~a catalog of \ncompanions\ companions for which the stellar companion
properties can be confidently determined in a posterior sense,
(2)~a catalog of stars that likely
have companions, but for which (in most cases) more observations
would be needed to uniquely
determine the orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all \nstars\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

>>>>

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting companions,
though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker)
that delivers reliable (and often highly
multi-modal) posterior samplings for companion orbital parameters given sparse
radial-velocity data.
% Aims
Here we
perform a search for secondary companions of over 100,000 red-giant
stars observed in the
\apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief about
the amplitude of the stellar radial-velocity variation induced by the orbit \todo{do we?}.
% Results
We provide (1)~a catalog of \todo{\ncompanions} companions for which the stellar companion
properties can be confidently determined in a posterior sense,
(2)~a catalog of stars \todo{YYY} stars that likely
have companions, but for which (in most cases) more observations
would be needed to uniquely
determine the orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all \nstars\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}
